Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-02-05 README.Rmd
updated readme

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428), Jacob Freeman, Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), Robert L. Kelly[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9737-0152), (2020). _`r Title`_. Under review.

>>>>

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), 
R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428),
Jacob Freeman [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7402-8450), 
Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), 
Robert L. Kelly[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9737-0152), 
(2020). _`r Title`_. Under review.
